### 2019-05-23 doc/chapters/towards_verifying.tex
rewrite inner class

>>>>

\subsection{Rewriting Private Inner Classes}
Stainless output (simplified):
\begin{lstlisting}
  [Warning ] CurrencyUnits.scala:36:3: Could not extract tree in class:
             case private class SatoshisImpl extends Satoshis
\end{lstlisting}
Stainless is not able to extract private classes inside other objects.
Bitcoin-S-core uses it a lot, because they separate the class from its implementation.
\begin{lstlisting}
  object Int64 extends BaseNumbers[Int64] {
    private case class Int64Impl(underlying: BigInt) extends Int64 
  }
\end{lstlisting}
This is an easy one.
Just extract the inner class out of the object.
This is not exactly the same code but since the class is still private it can not be extended outside of the file.
